### 2015-10-16 untitled.tex
add intro and many citations

\section{Introduction} 
This report revisits the \emph{period enforcer} algorithm proposed by Rajkumar \cite{Raj:suspension1991} to handle self-suspending real-time tasks. We briefly review the period enforcer algorithm, explain its underlying assumptions and limitations, and discuss how it may be analyzed to correctly determine the schedulability of self-suspending sporadic real-time tasks subject to period enforcement.

The main contributions of this paper are two observations that have not been previously reported in the real-time literature:

\begin{enumerate}
	\item period enforcement can render self-suspending tasks sets unschedulable that are schedulable otherwise (i.e., period enforcement can induce deadline misses); and
	\item with current techniques, schedulability analysis of the period enforcer algorithm requires a task set transformation that is subject to exponential time complexity.
\end{enumerate}

\subsection{Preliminaries}

@@

It is well known that uncontrolled deferred execution (i.e, release jitter) can impose a scheduling penalty because of the potential for ``back-to-back'' execution~\cite{ABRTW:93}. That is, if a job of a deferrable task that maximally defers its execution is directly followed by a job that executes immediately without deferring its execution, then lower-priority tasks may suffer increased interference.

@@

\subsection{Questions answered in this paper}

>>>>

\section{Introduction} 
When real-time task self-suspend (due to blocking I/O, lock contention, etc.), they defer a part of their execution to be processed at a later time. A consequence of such deferred execution is a potential interference penalty for lower-priority tasks~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}. This penalty, which is maximized when a task defers the completion of one job just until the release of the next job, can manifest as response-time increases and thus may lead to deadline misses.

To avoid such detrimental effects,  Rajkumar \cite{Raj:suspension1991} proposed the \emph{period enforcer} algorithm~\cite{Raj:suspension1991},  a technique to control (or shape) the processor demand of self-suspending tasks. In a nutshell, the period enforcer algorithm artificially increases the length of certain suspensions whenever a task's activation pattern carries the risk of inducing undue interference in lower-priority tasks.

The period enforcer algorithm is worth a second look for a number of reasons. First, in the words of Rajkumar, it ``forces tasks to behave like ideal periodic tasks from the scheduling point of view with no associated scheduling penalties''~\cite{Raj:suspension1991}, which is obviously highly desirable in many practical applications in which self-suspensions are inevitable (e.g., when offloading computations to co-processors such as GPUs or DSPs). Second, the later-proposed, but more widely-known \emph{released guard} algorithm~\cite{SL:96} uses a technique quite similar to period enforcement to control scheduling penalties due to release jitter in distributed systems. The period enforcer algorithm has also attracted growing attention  and has been mentioned in several recent works  (e.g.,~\cite{LNR:09,LR:10,Lak:11,LC:14,KANR:13,HY:11,CA:09,CA:10,CA:10b}), at times controversially~\cite{BA:08a}. And last but not least, the period enforcer algorithm plays a significant role in Rajkumar's seminal book on   real-time  synchronization~\cite{Raj:91}.

In this note, we revisit the period enforcer \cite{Raj:suspension1991} to carefully re-examine and explain its underlying assumptions and limitations, and to point out potential misconceptions.  The main contributions are three observations that, to the best of our knowledge, have not been previously reported in the real-time literature:
\begin{enumerate}
	\item period enforcement can be a cause of deadline misses in self-suspending tasks sets that are otherwise schedulable (Section~\ref{sec:unschedulable}); 
	\item with current techniques, schedulability analysis of the period enforcer algorithm requires a task set transformation that is subject to exponential time complexity (Section~\ref{sec:convert}); and
	\item the period enforcer algorithm is incompatible with all existing analyses of suspension-based locking protocols, and can in fact cause ever-increasing suspension times until a deadline is missed (Section~\ref{sec:locking}).
\end{enumerate}

We briefly introduce the needed background in Section~\ref{sec:prelim}, restate our contributions more precisely in Section~\ref{sec:questions}, and then explain the three above  observations in detail in Sections \ref{sec:unschedulable}--\ref{sec:locking} before concluding in Section \ref{sec:conclusion}.

\subsection{Preliminaries}
\label{sec:prelim}

@@

It is well known that uncontrolled deferred execution (i.e, release jitter) can impose a scheduling penalty because of the potential for ``back-to-back'' execution~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}. That is, if a job of a deferrable task that maximally defers its execution is directly followed by a job that executes immediately without deferring its execution, then lower-priority tasks may suffer increased interference.

@@

\subsection{Questions answered in this paper}
\label{sec:questions}
